Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-02-27 writeups/psycMethodsResponse/response.tex

\question (2b) how exploratory findings inform ACT-R in its instantiations and perhaps even in qualifications/revision to the theory -- there is a balance to strike here: the paper should be a highly accessible example of combining theory with big data (continuing to clarify for the reader -- e.g., Rev 2, para 6, 8, 9), ...

\begin{solution}
Was addressed in the reviewer's comment.
\end{solution}

\question … yet technical details are also important for those with more serious investments in ACT-R; consider including technical details but relegating them to online Supplemental Material (which has no page limits, can be in color, etc.).

\begin{solution}
Provided a link to the github-hosted repository for this research.

``All software code created for this research is publicly available on GitHub (Stanley, 2014).''

@@

\question ...and perhaps research that combines group-level and individual phenomena in a multilevel framework of big-data modeling, analysis and inference (Rev 1, bullet 2)

\begin{solution}
Was addressed in reviewer's comment.
\end{solution}

\question 3. Closer consideration of optimized learning vs. ACT-R learning is warranted, where a reviewer suggests a hybrid approach in the literature that might suggest an important and needed shift in the framing, analysis and implications of the current work (Reviewer 1, bullet 7 -- also be sure to download Rev 1's hand-written PDF, where time is taken to suggest specific edits to the work)

\begin{solution}
Was addressed in reviewer's comment and suggested edits will be looked at and incorporated.
\end{solution}

@@

\question I would first like to commend the authors for an ambitious project. A high degree of scholarship is apparent in their work. Please see my attached review for in-line comments and suggestions. I would like to make some general points that I would like to see.

\begin{solution}
No need to comment
\end{solution}

\question - I found that the paper proceeded too quickly through the initial explanation of ACT-R and vector-based systems. This is especially important because the default version of ACT-R (6) was not described in detail (no Table or Figure was presented)

\begin{solution}
Added table and description for default version of ACT-R 6.

Expanded the section for the vector-based model and included a description of the retrieval process for that model.

Added a section that directly compares the theory of the vector-based and ACT-R model (``Comparison of Vector-Based Models and ACT-R'').
\end{solution}

@@

\question and no comparative figure outlining the differences in representation between ACT-R and vector-based systems was presented. I find the lack of discussion of the changes in the ACT-R architecture a major concern. The authors reference their prior work, but I believe it requires a separate section in the document to properly evaluate their current model's performance.

\begin{solution}
Added section that outlines the differences between ACT-R and vector-based systems (``Comparison of Vector-Based Models and ACT-R'').
\end{solution}

@@

\question - I found throughout the introduction and theory sections that the terminology seemed to waffle between discussion individual user's vs aggregate performance. It wasn't until the methods section that I realized it was due to the difference between how StackOverflow and Twitter information was obtained. I think some extra discussion on the psychological aspects of individual vs group psychology may make your argument stronger.

\begin{solution}
 Added a paragraph in discussion that addresses this and provides one future research idea.

 ``Individual vs. Group Representation of Memory. Even with the large datasets used in this research, there was not enough data on each individual user to build up separate co-occurrence matrices for them. That is, the context component of the declarative memory models used in this research was formed as a collection of observed co-occurrences across all individuals. Nonetheless, the prior component for the models was customized for each individual (except in the Twitter popular hashtags dataset when it was
not possible). Ideally, both components would be customized to the individual, and it remains an open question how much accuracy is influenced by using an aggregate or custom context component in the models.''
\end{solution}

@@

Expanded the section for the vector-based model and included a description of the retrieval process for that model.

Added a section that directly compares the theory of the vector-based and ACT-R model (``Comparison of Vector-Based Models and ACT-R'').
\end{solution}

\question - As I read through the paper, I found it unclear to maintain the exact thesis of the work? What is the goal of the research. While the amount of information collection was impressive, the paper came off much like 'throwing XXXX at the wall and seeing what sticks' rather than a targeted hypothesis of what should work and why. As such, the paper is more explanatory than predictive in the traditional sense, to its decrement since the paper is using cognitively-inspired models.

\begin{solution}
Added additional paragraph in introduction.

``As a general methodology for this research, we used a cognitively-constrained
exploratory model development process. Since we worked with large-scale datasets, we had enough data to explore many different modifications simultaneously without the risk of overfitting. However, we were not interested in bringing to bear the entire collection of machine learning algorithms to this prediction task in order to completely optimize a model. Rather, we were interested in evaluating how well two cognitive models could explain the results, and then making selective modifications to them to see how performance changes. The modifications that we explored were selected such that they influenced model accuracy, could be easily added to (or removed from) the cognitive models without massive modifications, and could be considered cognitively plausible.''
\end{solution}

\question - During the interpretation of the various results, I'm concerned that the graphs do not always accord with the discussion. In some cases, I noticed a small drop in accuracy was within the 95\%CI bounds between two conditions, making the difference statistically insignificant, however, these results are reported as being lower and a reason attributed (see p35 for an example). This greatly weakens the overall argument. I recommend performing some inferential statistics on the differences in performance to be sure that all reported effects are in fact significant. Even if they only trend a given way, it's important to note the size of the effect in your discussion.

\begin{solution}
Added section in general methodology describing the method of using CIs instead of explicit p-values throughout the paper.

``In similar spirit to Cumming and Finch (2005), Masson and Loftus (2003), Tryon (2001), confidence intervals were used throughout for statistical inference instead of explicit p-values. This was done because it is a more straightforward way to visualize all of the mean differences in accuracy (i.e., bar and line plots with a visual indication of the error) for each of the models, which eases interpretation. It is also a conservative estimate of
reliability, as using confidence intervals on the means essentially ignores the fact that this is a within-subjects design, where accuracy for each model is measured for each subject in each dataset. However, we would rather err on the side of making the results easier to interpret at the cost of using conservative estimates for reliability (i.e., use error bars overlaid on a visualization of the means instead of statistical tests on every combination of difference scores). In fact, using large datasets for analysis is what empowers us to do this: With this much data, we can use straightforward (although more conservative) inferentials and still see reliable results. This allows us to concentrate more on proper data visualization of the main findings.
Nonetheless, when accuracy differences between two models are called out explicitly in the text, the confidence interval for the mean difference in accuracy is also included. Since this interval is drawn across the observed difference scores, it will be smaller than the intervals included in the plots, since these are drawn independently for each model’s overall accuracy.''

Added CI ranges over the difference scores for each of the model comparison accuracies that are written out.

e.g.: ``Accuracy for the hybrid form for the largest k (k = 10) is slightly higher than the smallest k (k = 1) (.334 vs. .329, mean difference = 0.0026, 95\% CI [0.0023, 0.0029]).''

Softened text on p35 since the fine-grained distinctions being made (although likely reliable if a more complicated and powerful statistical model was used to test them) were not necessary for the overall conclusions.

``Model accuracy as a function of co-occurrence matrix size for StackOverflow is depicted in Figure 11. Accuracy improves for both the Bayesian and random permutation models as the size of the documents used to generate the co-occurrence matrix increases. However for the random permutation model, accuracy begins to plateau for the largest corpus size for all three tested versions. The Bayesian model does not plateau nearly as much and accuracy continues to improve even at the largest measured corpus size.''

@@

\end{solution}

\question - I found the use of your entropy measure for attentional weight to be a key thesis of your paper and was intrigued by its use. I feel that this point could/should be expanded upon. What are the behavioral/cognitive consequences, what is its actual cognitive plausibility, why did you focus on attentional weight (Wj) instead of 'fixing' the Sji equation with some associative learning or the Bi with base-level inhibition? There was not a lot of discussion of other existing changes to the ACT-R architecture/theory that could potentially account for your data.

\begin{solution}
Expanded the discussion section for attentional weight and the entropy method

``Attentional Weight. The Bayesian declarative memory model for ACT-R has an attentional weight term Wj that can be used to attenuate or remove stop words. The random permutation model was also easily modified to have an attentional weight term by attenuating each word’s set of ones and negative ones values by that word’s attentional weight. Both a method for stop-word removal (frequency filtering) and stop-word attenuating (entropy weighting) performed well for both models.

It is unclear at this point if this modification is cognitively plausible, even if the modification was cleanly added to the current ACT-R model. What can be said from this research is that using a proper method for handling the low-predictor words produced some of the largest improvements in model accuracy compared to the other explorations (e.g., compared to word order or properly adding terms). Consequently, it may be worthwhile to explore this area more thoroughly in the future.

Also, there may be other ways besides adjusting the attentional weight that these models can be modified to achieve the same performance improvement. The entropy weighting term is likely solving a problem that resides only in contextual activation and not prior activation, since the activation for the prior component for each word is independent of the presentation of other words, so stop words have no way to interact with tag prior activation in this case.

One alternative explanation is that the entropy weighting measure was needed because the contextual co-occurrence matrix was not yet stable, even with these large dataset sizes. If the matrix was not yet stable, then by chance certain stop words would contribute more net activation to specific tags and introduce noise into the retrieval process for that tag. So further weighting the contribution of these stop words by leveraging the attentional weight term ensured that this noise was suppressed in the system. If this is the case, it would be interesting to see how large a dataset is required to not need to modify the attentional weight term. However even if this is the case, the random permutation model would still require entropy weighting for larger dataset sizes, since this model simply adds environment vectors to produce the current context vector and has no mechanism (unlike Bayesian normalization) for weighting the contribution of an environment vector.

Another explanation for the Bayesian model is that additional attentional weighting was needed because the contextual matrix was derived only from word by tag co-occurrences and not (word or tag) by (word or tag) co-occurrences. This was done for performance reasons as the computational complexity otherwise is simply too high for current hardware. It is possible that by adding all pairwise combinations of both words and tags in the posts may soften and stabilize the contribution of stop words when computing contextual activation for a tag, given current context.

Also perhaps a different Sji model may not need entropy weighing at all (e.g., the Hebbian-inspired associative learning model described in Thomson and Lebiere, 2013). Further research could explore how entropy weighting interacts with other models of Sji, and not just the random permutation and full Bayesian model.

Nonetheless, it seems likely that the entropy method for computing the attentional weight term Wj may be applicable to other declarative memory tasks. The entropy method is parameter-free (unlike the frequency-filtering method), completely data driven (much like the co-occurrence matrix), does not require tuning, and increases model accuracy for these datasets. It is common to handle stop words in some manner when working with Natural Language Processing (NLP) and large text corpuses. So, if these large corpuses are used to test declarative memory, then the entropy method may be a more cognitively plausible way of dealing with stop words rather than filtering based on a predetermined list or the frequency count in the dataset.''

@@

\end{solution}

\question - I was also a bit concerned with the dichotomy between optimized learning and full-on ACT-R learning. Most models that I've ever written (and everyone else I've collaborated with) use ACT-R's hybrid optimized learning equation that remembers the last 5 or 10 references and then averages the rest. This keeps the model computationally efficient while still having the benefits of local spikes in activation due to local high-frequency events (something you'd see in twitter or StackOverflow during conversations). It seems an oversight to have not tested the optimal hybrid equation. It should be relatively easy for you to run your model varying that parameter and report (briefly) on the results. This could potentially drastically change your interpretation of when to use Bayesian vs vector-based models... which was a section I found specious to begin with.

\begin{solution}
Ran the hybrid form with k=1,5,10 and incorporated the results into the past user behavior section.

``However the hybrid form with a reasonable k is just as accurate as the standard form. This is due to the fact that the majority of change in activation for a chunk occurs in the short period of time after the presentation of the chunk (a property of a power law distribution). Once a chunk’s presentations decay to the flat area of the power law distribution, not much change in activation for these presentations occurs, so they can be averaged and their presentation time can be discarded without much loss in fidelity. Therefore if computational speed is a concern, one may wish to leverage the hybrid form instead of the standard form. Although qualitatively the standard form produces the cleanest and most natural effect of decay rate on accuracy, as shown in Figure 1. It also does not have a bifurcation at k = 1. Consequently, if one is a purist and computational speed is less of a concern, one may still wish to use the standard form over the hybrid form.''

@@

\end{solution}

\question - This may be a copy-editing issue, but I think the heading levels need to be adjusted. It makes some points (see Word Order in the theoretical background) a bit unclear.

\begin{solution}
Heading level was as intended, but reworded the heading to make it more explicit that the section was a subsection of vector-based memory systems.
\end{solution}

@@

\question - From personal preference, I find too many sentences starting with "So" when no conclusion is made. This is made worse since many sentences proceeding "So" then start with "Thus" or "Then". This is stylistic but there are numerous places where phrasing comes off as too informal or 'train-of-thought'.

\begin{solution}
Removed most of them, particularly the ones that were used to start a new paragraph or the ones that the reviewer highlighted in the marked document. I left a few as I prefer them stylistically over overuse of ‘consequently’, ‘therefore’, ‘thus’, etc.
\end{solution}

### 2016-02-27 writeups/psycMethodsResponse/response.tex

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}
\definecolor{SolutionColor}{rgb}{0.1,0.3,1}
\usepackage{lipsum}
\usepackage{enumerate}
\usepackage{alphalph}

\renewcommand{\theenumi}{\AlphAlph{\value{enumi}}}
\renewcommand{\thequestion}{\AlphAlph{\value{question}}}
\renewcommand\questionlabel{\llap{\thequestion)}}

%\pointsinrightmargin
%\boxedpoints
\unframedsolutions
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.9,0.9,1}
\renewcommand{\solutiontitle}{}

% http://tex.stackexchange.com/questions/36423/random-unwanted-space-between-paragraphs
\raggedbottom

@@

\begin{document}

To Lisa	Harlow and Fred	Oswald,	co-editors, \bigskip

Please see below our responses to the reviewer comments.
Along with pasting text from the revised document inline with the questions where applicable,
I have also attached a version of the .pdf that contains markup for the differences between the original and revised submission. \bigskip

We hope that you and the reviewers find these changes sufficient and that you find the revised document well suited for this special issue. \bigskip

Respectfully,

-Clayton Stanley

\bigskip
\bigskip

@@

\question ...and perhaps research that combines group-level and individual phenomena in a multilevel framework of big-data modeling, analysis and inference (Rev 1, bullet 2)

\begin{solution}
Was addressed in reviewer's comment.
\end{solution}

\question 3. Closer consideration of optimized learning vs. ACT-R learning is warranted, where a reviewer suggests a hybrid approach in the literature that might suggest an important and needed shift in the framing, analysis and implications of the current work (Reviewer 1, bullet 7 -- also be sure to download Rev 1's hand-written PDF, where time is taken to suggest specific edits to the work)

\begin{solution}
Was addressed in reviewer's comment and suggested edits were looked at and incorporated.
\end{solution}

@@

\question and no comparative figure outlining the differences in representation between ACT-R and vector-based systems was presented. I find the lack of discussion of the changes in the ACT-R architecture a major concern. The authors reference their prior work, but I believe it requires a separate section in the document to properly evaluate their current model's performance.

\begin{solution}
Added section that outlines the differences between ACT-R and vector-based systems (``Comparison of Vector-Based Models and ACT-R'').
\end{solution}

\question - I found throughout the introduction and theory sections that the terminology seemed to waffle between discussion individual user's vs aggregate performance. It wasn't until the methods section that I realized it was due to the difference between how StackOverflow and Twitter information was obtained. I think some extra discussion on the psychological aspects of individual vs group psychology may make your argument stronger.

\begin{solution}
 Added a paragraph in discussion that addresses this.

@@

\end{solution}

\question - I was also a bit concerned with the dichotomy between optimized learning and full-on ACT-R learning. Most models that I've ever written (and everyone else I've collaborated with) use ACT-R's hybrid optimized learning equation that remembers the last 5 or 10 references and then averages the rest. This keeps the model computationally efficient while still having the benefits of local spikes in activation due to local high-frequency events (something you'd see in twitter or StackOverflow during conversations). It seems an oversight to have not tested the optimal hybrid equation. It should be relatively easy for you to run your model varying that parameter and report (briefly) on the results. This could potentially drastically change your interpretation of when to use Bayesian vs vector-based models... which was a section I found specious to begin with.

\begin{solution}
Ran the hybrid form with k=1,5,10 and incorporated the results into the past user behavior section.

``However the hybrid form with a reasonable k is just as accurate as the standard form. This is due to the fact that the majority of change in activation for a chunk occurs in the short period of time after the presentation of the chunk (a property of a power law distribution). Once a chunk's presentations decay to the flat area of the power law distribution, not much change in activation for these presentations occurs, so they can be averaged and their presentation time can be discarded without much loss in fidelity. Therefore if computational speed is a concern, one may wish to leverage the hybrid form instead of the standard form. Although qualitatively the standard form produces the cleanest and most natural effect of decay rate on accuracy, as shown in Figure 1. It also does not have a bifurcation at k = 1. Consequently, if one is a purist and computational speed is less of a concern, one may still wish to use the standard form over the hybrid form.''

@@

Reviewer 2:

\question The authors set out to explore large scale "tagging" datasets with the motivation: "Without using large datasets it is difficult to verify and explore modifications to the declarative memory architecture because the datasets are not large enough or rich enough to rigorously test modifications to the theory."

This certainly did wet the present readers appetite, but unfortunately after reading the manuscript, still starving for clearly defined models, testable predictions, or clear conclusions.

\begin{solution}
  Specific issues were addressed in the following comments from the reviewer.
\end{solution}

@@

Expanded the section for the vector-based model and included a description of the retrieval process for that model.

Added a section that directly compares the theory of the vector-based and ACT-R model (``Comparison of Vector-Based Models and ACT-R'').
\end{solution}

\question With respect to the data I think availability is a strong argument. However, there are strong limitations to observational data compared to active experiments (i.e. controlling for message differences by letting multiple users tag the same message)

\begin{solution}
Added a paragraph in the discussion section.

``Observational vs. Experimental Design. All data used for this study were collected from publicly-available datasets and were not subject to an experimental design
(i.e., observational data). There are advantages and disadvantages to both observational and experimental designs. One primary advantage with the observational approach here is size and availability: data for millions of posts and tweets are immediately available for analysis. However one disadvantage is that there is no way to probe a user at a particular point in time, which could be quite advantageous for answering certain questions. One hybrid approach worth considering for future research is to use the publicly available datasets to build up a representation of declarative memory for each user. Afterwards, bring a sample of these specific users into a laboratory setting and probe them with specific retrieval requests. Multiple users could be asked to tag the same message, and then models could be tested to see if they reliably predict differences in accuracy between the subjects.''
\end{solution}

@@

\question The design description lacks crucial details: "Each model was tested by evaluating the accuracy of model-chosen tags on a fresh test subset of the datasets." How was it (sub-)sampled? what was the size?

\begin{solution}
  Removed this text at this point, as it was leading the reader to think that I was about to provide more detail about how the sampling was done, and this detail is provided in line for each subsection. For example, much text to follow explicitly defines how each dataset was sampled, and then the methods section for combining prior and context defines how the test data are randomly sampled (including size) apart from the training data, and calls out that data in the test sets are not included to build the co-occurrence matrices.
\end{solution}

@@

\question More importantly I am in serious doubt of the relevance of tagging for "declarative memory". Tagging can best be seen as social behavior/communication. Hence the communication network appears crucial for understanding tag behavior. Specifically, the behavior of the recipient appears crucial to me. In StackOverflow the aim is to get an answer, hence, the main purpose is to get attention from experts, which is more related to expected behavior of the recipient rather than a memory issue. Similarly for Twitter. This issue should at least be discussed.

\begin{solution}
Added a paragraph in the discussion section.

``Tagging as a Declarative Memory Retrieval Process. Overall, both the random permutation and Bayesian declarative memory models fit the observed tagging behavior in StackOverflow and Twitter reasonably well. The fits for StackOverflow in particular are quite high, especially given the large tag space on the site.

These results provide support for the idea that choosing a hashtag when composing a tweet and tagging a StackOverflow post is akin to a declarative memory retrieval process. However, both models are not 100 percent accurate, and the amount of variance left to predict is larger than what would be observed if retrieval noise is included in the model. One possibility that seems likely is that the tag selection process includes other processes besides just declarative memory retrieval (e.g., strategic processes, determining the number of tags to employ, attempts to add humor).

Another possibility is that this is not a declarative memory process at all. In particular, it is important to note that tagging on these sites is widely used as a method to communicate specific messages to specific groups of people in the community. It is unclear how much this environment overlaps with verbal communication between two people, and the declarative memory requests required to successfully communicate in this setting. Nonetheless, these models are reasonably accurate in this setting, particularly for StackOverflow. Given the results in this research, it at least seems worthwhile to use these publicly-available tagging environments as a reasonable proxy to explore and validate modifications to the current theory.''

@@

\end{solution}

\question It is also not so clear what we have learned from the small differences in performance - can it be explained by differences in model complexity or does it reflect genuine differences in the models of declarative memory?

\begin{solution}
Added a paragraph in the discussion section.

``Directly Comparing the Models. After including the prior and entropy components for both models, overall accuracy was similar for the Bayesian and random permutation models for this task. So it is unclear precisely which model is more cognitively plausible (or if both are correct and simply working at different levels of abstraction). However, there were two areas in particular where model performance showed relatively large differences: accuracy change as a function of corpus size and reliance on entropy weighting. These areas could be used in future research to more directly challenge the models. For example, a domain could be picked where enough data is collected to build a custom co-occurrence matrix for each user. Then one could look at model accuracy over time for each user as the co-occurrence matrix is increased to see if the trajectory is more accurately modeled by a random permutation (more accurate with lower N) or Bayesian (more accurate with higher N) model. Further, if a large-scale domain is picked and it is shown that the Bayesian model does not require entropy weighting for the co-occurrence matrix after the representations are fully stabilized, then this would provide a case where the two models are dramatically different: The random permutation model would require explicitly weighting the stop words (entropy weighting) while the Bayesian model would not.''

@@

\end{solution}

\question It is well known that tags follow heavy tailed (powerlaw) distributions. Hence, normalization and sampling are critical issues. Here we learn "Each model was tested by evaluating the accuracy of model-chosen tags on a fresh test subset of the datasets." How was the test data (sub-)sampled? what were their size and time ordering, how was the tag space controlled /stratified for the test sets?

\begin{solution}
Removed this text at this point, as it was leading the reader to think that I was about to provide more detail about how the sampling was done, and this detail is provided in line for each subsection. For example, much text to follow explicitly defines how each dataset was sampled, and then the methods section for combining prior and context defines how the test data are randomly sampled (including size) apart from the training data, and calls out that data in the test sets are not included to build the co-occurrence matrices.

@@

\end{solution}

\question The English is excellent, however the writing could be made considerably more precise; e.g. by clearly defining central concepts, such as "chunk".

\begin{solution}
Added a definition of ‘chunk’ prior to its first use.

``ACT-R (Anderson, 2007) is a cognitive architecture that formalizes how each cognitive process of the mind (e.g., memory, learning, visual and motor) interacts to produce behavior. The declarative memory system is a component of the architecture that models the timing, learning, and forgetting processes that make up declarative memory storage and retrieval. At the core of the system is the concept of a “chunk”: the representation of a piece of knowledge (e.g., a word).''

### 2016-06-06 writeups/psycMethodsResponse2/response.tex

\documentclass[answers,12pt]{exam}
\usepackage{xcolor}
\definecolor{SolutionColor}{rgb}{0.1,0.3,1}
\usepackage{lipsum}
\usepackage{enumerate}
\usepackage{alphalph}

\renewcommand{\theenumi}{\AlphAlph{\value{enumi}}}
\renewcommand{\thequestion}{\AlphAlph{\value{question}}}
\renewcommand\questionlabel{\llap{\thequestion)}}

%\pointsinrightmargin
%\boxedpoints
\unframedsolutions
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.9,0.9,1}
\renewcommand{\solutiontitle}{}

% http://tex.stackexchange.com/questions/36423/random-unwanted-space-between-paragraphs
\raggedbottom

\begin{document}

To Lisa	Harlow and Fred	Oswald,	co-editors, \bigskip

Please see below our responses to the reviewer comments.
Along with pasting text from the revised document inline with the questions where applicable,
I have also attached a version of the .pdf that contains markup for the differences between the original and revised submission. \bigskip

We hope that you and the reviewers find these changes sufficient and that you find the revised document well suited for this special issue. \bigskip

Respectfully,

-Clayton Stanley

\bigskip
\bigskip

\begin{questions}

\question Primary concern: Papers on predictive modeling typically avoid confidence intervals and instead seek to optimize out-of-sample RMSE or R2 based on training vs. test samples (e.g., k-fold cross-validation) or sometimes by resampling (bootstrapping); see overviews of predictive modeling such as http://www-bcf.usc.edu/~gareth/ISL/ and http://appliedpredictivemodeling.com/.  The general concern here is that people reading your paper alongside other 'big data' papers may view your confidence interval approach unusual or outdated; the more specific concern here is overfitting the model to the data (making confidence intervals too confident).

\begin{solution}
No need to comment directly.
\end{solution}

\question Lesser concern: Per Rev 3 para 3, consider how prediction might increase when methods dynamically afford an increase in model dimensionality whenever the size of a corpus increases (this could be considered in terms of differences in sizes across corpora and/or across users). It is fine if you simply point this out as future research in your concluding statements, although an example could be incorporated if you so desired. Your choice.

\begin{solution}
No need to comment directly.
\end{solution}

\question Lesser concern: Per Rev 3, para 5 and 7, please incorporate any additional relevant literature (but do not limit yourself to Rev 3 citations; check out what is current and relevant given this quickly changing phenomenon and research area).

\begin{solution}
No need to comment directly.
\end{solution}

\question If you have not already done so as part of your Author Note, please provide the details (2-4 sentences) of prior dissemination of the ideas and data appearing in the manuscript (e.g., if some or all of the data and ideas in the manuscript were presented at a conference or meeting posted on a listserv, shared on a website, etc.).

\begin{solution}
No need to comment directly.
\end{solution}

Reviewer 3:

\question The counterintuitive results are also intriguing (such as the finding that larger training corpora lowered performance for the random permutations models). However, one factor to consider is that RP models depend on the approximate orthogonality of the random projections (the environment vectors for Beagle). As the number of words increases, this will tend to oversaturate the space, and commonly leads to decreased performance. One standard approach here is to scale the dimensionality of the representations as the training set and vocabulary sizes increase. It would be interesting to see if the performance still leveled off if you increased the dimensionality with the corpus size.

\begin{solution}
\end{solution}

\question A number of works have considered the large scale dynamics of hashtag use (e.g. ``\#Bigbirds Never Die: Understanding Social Dynamics of Emergent Hashtags'', 2013), while other work has looked specifically at the impact of tags used by a user's local network connections (``We know what @you \#tag: does the dual role affect hashtag adoption?'', 2012). There is an extensive literature exploring how user features including demographics (e.g. ``User Conditional Hashtag Prediction for Images'', 2015), prior posts, time of day, mood, etc. The relationship between this literature and the work presented in the paper needs to be discussed thoroughly.

\begin{solution}
\end{solution}

\question While the authors discuss that declarative memory might not be the correct model for this task (p 51-52), this seems to be almost an afterthought. Given that there is a flourishing literature which goes beyond this narrow focus, it seems important to acknowledge that upfront in the paper.

\begin{solution}

\end{solution}

\question That said, declarative memory retrieval is still likely to be a critical part of this process and worth exploration on its own. As such, the paper can still work even without incorporating any of those additional features. Many papers in this area report whether not just whether the tag from the model was predicted, but also whether it was in the top n (10, 25, etc) most likely predictions returned by the model (for one example of this, see ``\#TAGSPACE: Semantic Embeddings from Hashtags'', 2014). One possibility would be to treat the declarative memory portion (modeled here) as generating candidates which other processes consider.

\begin{solution}

\end{solution}

\question Questions of cognitive plausibility were also present in the structure of some of the pre-processing techniques used. While the authors acknowledge this, it would have been helpful to see more about how they felt that non-cognitive modeling or standard NLP techniques can help us to better understand and refine the underlying cognitive models. At very least acknowledging this intersection would have helped to eliminate some of the sense that the paper occasionally veered between claims of cognitive plausibility and more conventional computational modeling.

\begin{solution}
\end{solution}

\end{questions}

\end{document}

### 2016-06-06 writeups/psycMethods/psycMethods.tex
foo

>>>>

\subsection{Compression Level for Random Permutation}

Another parameter in the random permutation model is the number of rows used to represent all of the different words.
Each word's environment vector is represented by two randomly placed ones and two negative ones across the rows.
All that is required is that the four positions and signs of each of these environment vectors is unique.
But this means multiple environment vectors can overlap when looking at a single row.
This is a lossy form of compression, and allows the number of rows to represent the words to be much less than the total number of words.
As the number of rows decreases, the amount of cross talk between the environment vectors increases, compression increases, and the amount of information stored decreases.
As a third architectural concern, the effect of compression for the random permutation model was examined for Twitter and StackOverflow.

Three different row-size values were tested for the random permutation model to see how accuracy changed as a function of space required to represent the co-occurrence matrix.
A low value (\num{100}), a more standard value (\num{2048}), and a high value (\num{10000}) of rows were tested.
A separate co-occurrence representation was built for each of these row values.
Each representation was tested on the four Twitter popular-hashtags datasets and the StackOverflow randomly-sampled dataset.
Accuracy measurements were the same as were used for previous runs of these datasets: mean accuracy for each of the 5 StackOverflow and 15 Twitter runs.

Results for using different levels of compression for the random permutation model for the StackOverflow dataset are depicted in Figure \ref{figContextDimSO}.
In the figure, the model name that does not have the number of rows in the matrix specified is the \num{2048}-row matrix.
This was done so that names in all of the plots would remain consistent across all plots, and the \num{2048}-row matrix is the size used for the random permutation model for all other results.
The plot is also broken out for different size datasets used to build the co-occurrence matrix.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-dimBySizeSO-crop.pdf}}}
  \caption{
    Effect of compression on random permutation model for StackOverflow.
    Error bars represent the 95\% bootstrapped confidence interval for the mean.
  }
  \label{figContextDimSO}
\end{figure}

Reducing compression to only 100 rows in the representation has a strong negative effect on accuracy, which shows that compression can influence model accuracy.
However, \num{2048} rows is sufficient for these datasets, as increasing the number of rows to almost an order of magnitude higher (\num{10000}) has little to no positive impact on accuracy, even for the highest corpus sizes.

Results are similar for Twitter.
Figure \ref{figContextDimT} shows the same negative impact when reducing from \num{2048} to \num{100}, and little to no impact when increasing from \num{2048} to \num{10000}. 
These results are consistent across all corpus sizes used to build the co-occurrence matrix.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-dimBySizeT-crop.pdf}}}
  \caption{
    Effect of compression on random permutation model for Twitter.
    Error bars represent the 95\% bootstrapped confidence interval for the mean.
  }
  \label{figContextDimT}
\end{figure}

The fact that the random permutation model only needs around \num{2048} rows to represent all of the words in the Twitter and StackOverflow datasets is impressive.
Twitter has around \num{2383000} unique words for the \num{3000000} tweets in each of the popular-users datasets.
StackOverflow has \num{5848000} unique words for the \num{1000000} posts used to generate the co-occurrence matrix.
So it is impressive that only \num{2048} rows are needed to represent most of the variance from all of the words in these co-occurrence matrices.
This is likely because word use frequency for StackOverflow and Twitter approximately follows Zipf's law.
\textcite{Stanley2013} showed that frequency of tag use for StackOverflow approximately follows a Zipf's law distribution.
This means that if the words are rank sorted by number of times they are used, the frequency of word use drops off sharply when moving to words that are used fewer times.
Since these words have little to no ability to influence predictions, it makes sense that they can be safely removed from the dataset.
